SPARQL on the Open, Decentralised Web

### 2016-07-27 dissertation/cache-proxy.tex
Clean out my own stuff from HERMES and move some

>>>>

It is further interesting to note the contrast to the HERMES
\cite{adali1996query} system's concept of invariants discussed in
Section~\ref{sec:relcache}: a SPARQL query cache should be oblivious
to domain knowledge and therefore shouldn't assume any invariants,
except in the possible but unlikely case where the remote server
declares an infinite freshness lifetime for the result of a certain
graph pattern.

### 2016-07-27 dissertation/related.tex
Clean out my own stuff from HERMES and move some

HERMES \cite{adali1996query} provided motivation for the paper in
Section~\ref{sec:conpush}, but is also important for the
work in Chapter~\ref{sec:tpfcacheplanning}. An important concept in
the HERMES system is ``invariants''. They are, in our terminology,
patterns that do not need to be looked up remotely, but can be
integrated in the query answer by the mediator. The expectation in
HERMES is that such invariants will be encoded by a domain expert. The
Attean framework, which is used extensively in my work and is
detailed in Section~\ref{sec:attean} provides facilities to do this in
an easy and extensible way, and also accommodates for the task of
computing a scalar cost metric, but HERMES has a more advanced cost
model in that it has a cost vector with estimates for time required to
find the first answer, time to find all answers and the cardinality of
the answer set. Caching summary statistics is another important
feature of HERMES, and it also contributes lossy and lossless
summaries, for the purpose of saving space and reduce the time it
takes to compute a cost estimate. HERMES further has a query rewriter
and optimiser, that rewrites the query taking into account the cache
and the invariants. While HERMES is more general than what I detail in
Chapter~\ref{sec:tpfcacheplanning}, we note that while invariants
could be coded in Attean, a SPARQL query cache should be oblivious to
domain knowledge and therefore shouldn't assume any invariants, except
in the possible but unlikely case where the remote server declares
an infinite freshness lifetime for the result of a certain graph
pattern. While statistics summarisation is relevant and should be
studied in future work, we note that with a Linked Data Fragments
server, a cardinality estimate is required to be available for every
triple pattern, and is also cacheable with the same constraints as the
data themselves.

>>>>

HERMES \cite{adali1996query} provided motivation for the paper in
Section~\ref{sec:conpush}, but is also important for the work in
Chapter~\ref{sec:tpfcacheplanning}. An important concept in the HERMES
system is ``invariants''. They are, in our terminology, patterns that
do not need to be looked up remotely, but can be integrated in the
query answer by the mediator. The expectation in HERMES is that such
invariants will be encoded by a domain expert. The HERMES planner
bases decision on a cost vector with estimates for time required to
find the first answer, time to find all answers and the cardinality of
the answer set. Caching summary statistics is another important
feature of HERMES, and it also contributes lossy and lossless
summaries, for the purpose of saving space and reduce the time it
takes to compute a cost estimate. HERMES further has a query rewriter
and optimiser, that rewrites the query taking into account the cache
and the invariants. While statistics summarisation is relevant and should be
studied in future work, we note that with a Linked Data Fragments
server, a cardinality estimate is required to be available for every
triple pattern, and is also cacheable with the same constraints as the
data themselves.
